---
title: 'Realtime ILI forecasting report: Massachusetts'
author: "Graham Casey Gibson, Nicholas Reich, Evan Ray"
date: "3/28/2019"
output: pdf_document
---

# Intro
The Reichlab produces weekly forecasts of the percentage of doctors visits that present with influenza-like-illness (ILI) at the state level based on data provided through the CDC Flusight challenge. We use historical ILI incidence to predict future ILI incidence using statistical models. 

# MA Results
What follows is the forecasted 1-4 week ahead ILI along with 50% and 80% confidence interval around the forecasts. 

```{r,echo=FALSE, include=FALSE}

get_ci_from_sample <- function(dist,level){
  
  
  total_mass <- 0
  start_index <-   which.max(dist)
  left_index <- start_index
  right_index <- start_index
  while(total_mass <level){
    if (left_index >= 1 & right_index <= length(dist)){
      if (left_index == start_index){
        total_mass <- total_mass + dist[start_index]
      } else{
              total_mass <- total_mass  + dist[left_index] + dist[right_index]
      }
      left_index <- left_index - 1
      right_index <- right_index + 1
    
    } else if (left_index == 0 & right_index <= length(dist)){
      total_mass <- total_mass + dist[right_index]
   } else if (right_index == length(dist) & left_index >=1){
        total_mass <- total_mass + dist[left_index]
   }
  }
  return (c(left_index/10,right_index/10))
}



library(ggplot2)
library(cdcFlu20182019)
data <- download_and_preprocess_state_flu_data()
data_ma <- data[data$region == "Massachusetts",]

current_epiweek <- tail(data$week,1)
current_season <- tail(data$season,1)


#model_csv <- read.csv(paste0("../../submissions/state-sarima/EW",current_epiweek,"-KoT-StateILI-",ymd(Sys.Date()),".csv"))
model_csv <- read.csv(paste0("../../submissions/state-sarima/EW",11,"-KoT-StateILI-2019-03-25",".csv"))


k_step_ahead <- c(model_csv[model_csv$Location=="Massachusetts" & model_csv$Target == "1 wk ahead" & model_csv$Type == "Point",]$Value,
                  model_csv[model_csv$Location=="Massachusetts" & model_csv$Target == "2 wk ahead" & model_csv$Type == "Point",]$Value,
                  model_csv[model_csv$Location=="Massachusetts" & model_csv$Target == "3 wk ahead" & model_csv$Type == "Point",]$Value,
                  model_csv[model_csv$Location=="Massachusetts" & model_csv$Target == "4 wk ahead" & model_csv$Type == "Point",]$Value
                  )

k_step_ahead_quantile_80 <- c(get_ci_from_sample(model_csv[model_csv$Location=="Massachusetts" & model_csv$Target == "1 wk ahead" & model_csv$Type == "Bin",]$Value,.8),
                  get_ci_from_sample(model_csv[model_csv$Location=="Massachusetts" & model_csv$Target == "2 wk ahead" & model_csv$Type == "Bin",]$Value,.8),
                  get_ci_from_sample(model_csv[model_csv$Location=="Massachusetts" & model_csv$Target == "3 wk ahead" & model_csv$Type == "Bin",]$Value,.8),
                  get_ci_from_sample(model_csv[model_csv$Location=="Massachusetts" & model_csv$Target == "4 wk ahead" & model_csv$Type == "Bin",]$Value,.8)
                  )
upr_80 <- k_step_ahead_quantile_80[seq(0,length(k_step_ahead_quantile_80),by=2)]
lwr_80 <- k_step_ahead_quantile_80[seq(1,length(k_step_ahead_quantile_80),by=2)]


k_step_ahead_quantile_50 <- c(get_ci_from_sample(model_csv[model_csv$Location=="Massachusetts" & model_csv$Target == "1 wk ahead" & model_csv$Type == "Bin",]$Value,.5),
                  get_ci_from_sample(model_csv[model_csv$Location=="Massachusetts" & model_csv$Target == "2 wk ahead" & model_csv$Type == "Bin",]$Value,.5),
                  get_ci_from_sample(model_csv[model_csv$Location=="Massachusetts" & model_csv$Target == "3 wk ahead" & model_csv$Type == "Bin",]$Value,.5),
                  get_ci_from_sample(model_csv[model_csv$Location=="Massachusetts" & model_csv$Target == "4 wk ahead" & model_csv$Type == "Bin",]$Value,.5)
                  )
upr_50 <- k_step_ahead_quantile_50[seq(0,length(k_step_ahead_quantile_50),by=2)]
lwr_50 <- k_step_ahead_quantile_50[seq(1,length(k_step_ahead_quantile_50),by=2)]





```
```{r,echo=FALSE,warning=FALSE}
ggplot(data_ma[data_ma$season == "2018/2019",],aes(x=season_week,y=unweighted_ili)) + geom_point() + xlim(0,52)+ geom_line() +theme_bw() + xlab("Season Week") + ylab("ILI") + geom_vline(xintercept = tail(data$season_week,1),linetype="dashed") + geom_line(data=data.frame(y=c(tail(data_ma$unweighted_ili,1), k_step_ahead)),aes(x=(tail(data$season_week,1)):(tail(data$season_week,1)+4),y=y),col="cornflowerblue") +
  geom_point(data=data.frame(y=c(tail(data_ma$unweighted_ili,1), k_step_ahead)),aes(x=(tail(data$season_week,1)):(tail(data$season_week,1)+4),y=y),col="cornflowerblue") +
      geom_ribbon(data=data.frame(lwr=lwr_80,upr=upr_80,y= k_step_ahead),aes(x=(tail(data$season_week,1)+1):(tail(data$season_week,1)+4),ymin=lwr,ymax=upr,y=y),alpha=0.3,fill="cornflowerblue") + ggtitle("MA ILI") +
  geom_ribbon(data=data.frame(lwr=lwr_50,upr=upr_50,y= k_step_ahead),aes(x=(tail(data$season_week,1)+1):(tail(data$season_week,1)+4),ymin=lwr,ymax=upr,y=y),alpha=0.3,fill="cornflowerblue") +
geom_line(data=data_ma[data_ma$season == "2017/2018",],aes(x=season_week,y=unweighted_ili),alpha=.1)+
  geom_line(data=data_ma[data_ma$season == "2016/2017",],aes(x=season_week,y=unweighted_ili),alpha=.1)+
  geom_line(data=data_ma[data_ma$season == "2015/2016",],aes(x=season_week,y=unweighted_ili),alpha=.1)+
  geom_line(data=data_ma[data_ma$season == "2014/2015",],aes(x=season_week,y=unweighted_ili),alpha=.1)+
  geom_line(data=data_ma[data_ma$season == "2013/2014",],aes(x=season_week,y=unweighted_ili),alpha=.1)+
  geom_line(data=data_ma[data_ma$season == "2012/2013",],aes(x=season_week,y=unweighted_ili),alpha=.1)

```